Collaborative Infrastructure for Test-Driven \\Scientific Model Validation

### 2014-03-15 sciunit-icse14/sciunit-icse14.tex
ICSE14 final final

We argue that a similar test-driven methodology would be valuable to scientific communities as they seek to  validate increasingly complex models against growing repositories of empirical data. Scientific communities differ from software communities in several key ways, however. In this paper, we introduce \emph{SciUnit}, a framework for test-driven scientific model validation, and outline how, supported by new and existing collaborative infrastructure, it could be  integrated into the modern scientific process.
\end{abstract}
\category{D.2.5}{Software Engineering}{Testing and Debugging}%[complexity measures, performance measures]
\terms{Documentation, Measurement, Standardization}
\keywords{unit testing, model validation, cyberinfrastructure}

>>>>

We argue that a similar test-driven methodology would be valuable to scientific communities as they seek to  validate increasingly complex models against growing repositories of empirical data. Scientific communities differ from software communities in several key ways, however. In this paper, we introduce \emph{SciUnit}, a framework for test-driven scientific model validation, and outline how, supported by new and existing collaborative infrastructure, it could integrate into the modern scientific process.
\end{abstract}
\category{D.2.5}{Software Engineering}{Testing and Debugging}%[complexity measures, performance measures]
\terms{Documentation, Measurement, Standardization}
\keywords{unit testing, model validation, cyberinfrastructure}
